### 2014-06-06 paper/body.tex
small edits

Of course, this definition depends on the similarity, or distance, between \dA and \dB. In this paper, we take tasks \dA and \dB to be classifying different, non-overlapping subsets of a particular dataset.  These subsets could be chosen such that they are similar (e.g. by randomly splitting a large dataset into two smaller datasets), or they could be chosen to be different (e.g. by choosing the subsets to be maximally different). 
%This is only one possible way of sampling tasks \dA and \dB.

@@

All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section are the same, namely the sizes described in Section~\ref{} except for the last softmax layer, which outputs 500 classes instead of 1000.

>>>>

Of course, this definition depends on the similarity (distance) between \dA and \dB. In this paper, we take tasks \dA and \dB to be classifying different, non-overlapping subsets of a particular dataset.  These subsets could be chosen such that they are similar (e.g. by randomly splitting a large dataset into two smaller datasets), or they could be chosen to be different (e.g. by choosing the subsets to be maximally different). 
%This is only one possible way of sampling tasks \dA and \dB.

@@

All layer sizes in \net{baseA} and \net{baseB}, as well as the networks described later in this section, are the same, namely the sizes described in Section~\ref{} \todo{fill in this empty ref} except for the last softmax layer, which outputs 500 classes instead of 1000.
